### 2025-05-07 backmatter/solutions.tex
Completed problems and rough solutions

\iffalse
% ---------------------------------------
\Soln{Non-Perturbative Effects}{lqcd-nonpert}
% ---------------------------------------

% ---------------------------------------
\Soln{Leading Order Results for \texorpdfstring{\(e^+\,e^-\)}{electron-positron} to hadrons}{eetohadrons_lo}
% ---------------------------------------

First, let us recall the diagram for the process in question,
%
\begin{align}
    \tikzexdiagram{ee_to_qq}[0][1.3]
\end{align}
and recall the Feynman rules of QCD:
\sam{include}

Assuming all partons are massless and working in Feynman gauge,
\begin{subequations}
\begin{align}
    i \mathcal{M}_2^{(0)}
    &=
    \le(
    -i e_q
    \gamma^\mu
    \ri)
    \frac{i\eta_{\mu\nu}}{\le(p_1 + p_2\ri)^2}
    \le(
    -i e_q
    \gamma^\nu
    \ri)
    \\
    &=
\end{align}
\end{subequations}
\sam{missing spinor factors}
\sam{missing color factors}

% ---------------------------------------
\Soln{Next-to-Leading Order Results for \texorpdfstring{\(e^+\,e^-\)}{electron-positron} to hadrons}{eetohadrons_nlo}
% ---------------------------------------

% https://zzxianyu.com/wp-content/uploads/2017/01/peskin_problems.pdf#page=75

\begin{align}
    \tikzexdiagram{ee_to_qqg}[0][1.0]
\end{align}

\begin{align}
    \,.
\end{align}

\begin{align}
    \tikzexdiagram{ee_to_qq_loop}[0][1.5]
\end{align}

\begin{align}
    i \mathcal{M}_2^{(2)}
    =
    -i e
    \le(-i e_q\ri)
    \le(-i g_s\ri)^2
    \,\,
    \le(
    \gamma^\mu
    \ri)
    \,\,
    \frac{i \eta_{\mu\nu}}{\le(p_1 + p_2\ri)^2}
    \,\,
    \le(
        (T_F^a)\indices{^i_k}
        \,\,
        \gamma^\rho
        \,\,
        \frac{i \le(\slashed{k_1} + \slashed{\ell}\ri)}
            {\le(k_1 + \ell\ri)^2}
        \,\,
        \gamma^\nu
        \,\,
        \frac{i \le(\slashed{k_2} - \slashed{\ell}\ri)}
            {\le(k_2 - \ell\ri)^2}
        \,\,
        \gamma^\sigma
        \,\,
        (T_F^b)\indices{^k_j}
    \ri)
    \,\,
    \frac{i \delta_{ab} \eta_{\rho\sigma}}{\ell^2}
    \,.
\end{align}

% ---------------------------------------
\Soln{Kinematics for \texorpdfstring{\(e^+\,e^-\)}{electron-positron} to hadrons at NLO}{eetohadrons_kinematics}
% ---------------------------------------

% ---------------------------------------
\Soln{A Physical Approach to Plus-Functions}{physics-plus}
% ---------------------------------------

% ---------------------------------------
\Soln{Splitting Functions in Dimensional Regularisation}{dimreg-splitting}
% ---------------------------------------
\fi

@@

\begin{exercise*}
    Show that
    \begin{align}
        \abs{\Vec{k}'}
        =
        E'
        =
        E_n + E_{n-1} + \mathcal{O}\le(\theta^2\ri)
        ,
    \end{align}
    and use this to argue that, in the collinear limit, we can parameterize the energy dependence of the differential cross section into dependence on \(E'\) and on \(x\), where \(x\) is an \vocab{energy fraction} defined through
    \begin{align}
        E_n &= x E'
        \\
        E_{n-1} &= (1-x)E'
        .
    \end{align}
    Again, this will hold up to \(\mathcal{O}(\theta^2)\).
\end{exercise*}

@@

    \item
    \label{item:LL_angularity_gen}
    The splitting of a parton is described by its angularity \(e^{(f)}_\varsigma\).
    %
    Using the techniques of the previous section, we may write the LL probability that there is no emission with angularity greater than \(e^{(f)}_\varsigma\), given that there has been an emission with angularity \(e^{(i)}_\varsigma\), as
    \begin{align}
        \label{eq:alg_LLang_ratio}
        \mathbb{P}
        \left(
            {\rm no~emission~with~}e_\varsigma>e^{(f)}_\varsigma
            ~|~
            e_\varsigma < e^{(i)}_\varsigma
        \right)
        &=
        \frac{\Sigma(e^{(f)}_\varsigma)}{\Sigma(e^{(i)}_\varsigma)}
        \\
        \notag
        &=
        \exp\left[
            -\frac{C_R \alpha_s}{\varsigma~\pi}
            \left(
                \log^2(2 e^{(f)}_\varsigma) - \log^2(2 e^{(i)}_\varsigma)
            \right)
        \right]
        .
    \end{align}
    We can therefore sample from the corresponding probability distribution by the inverse transform method:
    %
    pick a random number \(r\) uniformly distributed between 0 and 1, and set it equal to the above cumulative distribution.
    %
    The corresponding value of \(e^{(f)}_\varsigma\) is
    \begin{align}
        \label{eq:alg_LLang}
        e^{(f)}_\varsigma
        =
        \frac{1}{2}
        \exp\left[
            -\sqrt{\log^2(2 e^{(i)}_\varsigma) - \frac{\varsigma~\pi}{C_R \alpha_s} \log(r)}
        \right]
        ,
    \end{align}
    which is taken to be the angularity of the splitting from this mother parton.

@@

We can also extend this procedure to include running coupling effects and non-singular pieces of the splitting function, which contribute to MLL accuracy.
%
We produce these higher-order effects by using veto method sampling \cite{Sjostrand:2007gs,Larkoski:2013paa,Sjostrand:2014zea}:
%
\begin{enumerate}
	\item
	\label{item:MLL_ps_start}
	Generate an angularity, angle, and energy fraction with Steps \ref{item:LL_ps_start}--\ref{item:LL_ztheta_sampling} of the LL parton shower algorithm, with the coupling \(\alpha_s\) of \Eqs{alg_LLang_ratio}{alg_LLang} replaced by a large fixed value for the coupling, \(\hat\alpha = \frac{1}{2}\).

	\item
	As dictated by the veto method, accept the generated variables with a probability given by the ratio \(\rho^{\rm(MLL)}(z,\theta)/\hat\rho^{\rm(LL)}(z,\theta)\), where \(\rho^{\rm(MLL)}\) indicates the MLL probability distribution function and \(\hat\rho^{\rm(LL)}\) indicates the LL probability distribution function with the coupling \(\hat\alpha\).
	%
	In particular, generate a new random number \(r''\) and accept the generated splitting if
	\begin{align}
	    r'' < \mathbb{P}_{\rm no~veto}
	    =
	    \frac{\bar{p}_i(z)}{p_{i,\,\rm gen}(z)}\,\frac{\alpha_s(\kappa)}{\hat\alpha}
	    ,
	\end{align}
	where \(p_{i,\,\rm gen}(z) = 2 C_{R_i} / z\) is the singular piece of the splitting function, used implicitly in drawing the angularity \(e_\varsigma^{(f)}\) from an LL distribution in \Eq{alg_LLang}.
	%
    The choice \(\hat \alpha = 1/2\) ensures that this probability is less than 1 if we freeze our coupling below the non-perturbative scale \(\mu_{\rm freeze}\) = 1 GeV.

@@

The cumulative distribution for the additive variable \(X\), including contributions from any number of emissions, is
\begin{align}
    \Sigma(x)
    &=
    \sum_{n = 1}^\infty \prod_{m = 1}^n
    \left[
        \int_0^{1} \frac{d\theta'_m}{\theta'_m}
        \int_0^1 dz_m p_i(z_m)
        \frac{\alpha_S(\kappa_m)}{\pi}
        \Theta(\theta_{m-1} - \theta_m)
        \Theta(z - z_c)
    \right]
    \,\,\,
    \Theta\left(x - \sum_{m=1}^n X(z_m, \theta_m)\right)
    \,.
\end{align}
The Laplace transform, \(\widetilde{f}(\nu) := \int_{-\infty}^\infty \dd x\, f(x) e^{-\nu x}\), of the cumulative distribution is therefore
\begin{align}
    \widetilde\Sigma(\nu)
    &:=
    \int_{-\infty}^\infty \dd x\, \Sigma(x) e^{-\nu x}
    \\
    &= \sum_{n=1}^\infty \prod_{m=1}^n  \left[
        \int_0^{1} \frac{\dd \theta'_m}{\theta'_m}
        \int_0^1 \dd z_m p_i(z_m)
        \frac{\alpha_S(\kappa_m)}{\pi}
        \Theta(\theta_{i-1} - \theta_i)
    \right]
    \,\,
    \int^\infty_{\sum X_m} \dd x \, e^{-v x}
    \\
    &=
    -\frac{1}{\nu}
    \,\,
    \sum_{n=1}^\infty \prod_{m=1}^n  \left[
        \int_0^{1} \frac{\dd \theta'_m}{\theta'_m}
        \int_0^1 \dd z_m p_i(z_m)
        \frac{\alpha_S(\kappa_m)}{\pi}
        \Theta(\theta_{i-1} - \theta_i)
        e^{-v X(z_m, \theta_m)}
    \right]
    \,.
\end{align}
Now we can take advantage of angular ordering, using Dyson's trick to replace the factors of \(\Theta(\theta_{i-1} - \theta_i)\) by a single factor of \(1 / n!\).
%
Using that the resulting features of the integrand have identical forms for each emission, this yields
\begin{align}
    \widetilde\Sigma(\nu)
    &=
    -\frac{1}{\nu}
    \,\,
    \sum_{n=1}^\infty \frac{1}{n!}
    \left(
        \int_0^{1} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alpha_S(\kappa)}{\pi}
        e^{-v X(z, \theta)}
    \right)^n
    \\
    &=
    -\frac{1}{\nu}
    \,\,
    \exp\le[
        \int_0^{1} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alpha_S(\kappa)}{\pi}
        e^{-v X(z, \theta)}
    \ri]
    \\
    &=
    -\frac{1}{\nu}
    \,\,
    \exp\le[
        \int_0^{1} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alpha_S(\kappa)}{\pi}
        \,
        \le(e^{-v X(z, \theta)} - 1\ri)
    \ri]
    \,,
\end{align}
where in the final equality we have used that \(p_i(z)\) integrates to zero in the soft-collinear limit.

Now we must invert the Laplace transform, via
\begin{align}
    \Sigma(x) = \int \frac{\dd \nu}{2\pi i} \, e^{\nu x} \widetilde\Sigma(\nu)
    \,,
\end{align}
to obtain the cumulative distribution for \(X\).
%
In particular we evaluate
\begin{align}
    \Sigma(x)
    =
    \int \frac{\dd \nu}{2\pi i\, \nu} \, e^{\nu x}
    \,
    \exp\le[
        \int_0^{1} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alpha_S(\kappa)}{\pi}
        \,
        \le(e^{-v X(z, \theta)} - 1\ri)
    \ri]
    \,,
\end{align}
by steepest descent.
\sam{sign?}

The stationary value of the integrand is \(\nu = 1 / x + \mathcal{O}(\alpha_s)\), so for small \(x\), \(\nu\) will be very large, and we can approximate
\begin{align}
    1 - e^{\nu X(z,\theta)}
    \approx
    1 - e^{X(z,\theta)/x}
    =:
    \Theta(X(z,\theta) - x) + \phi(x)
    \,
\end{align}
as roughly equal to a Heaviside theta function, i.e. that \(\phi(x) := 1 - e^{X(z,\theta)/x} - \Theta(X(z, \theta) - x)\) is small for large values of \(\nu\).
%
We can therefore use the radiator for \(X\) to simplify our results, noting that
\begin{align}
    \int_0^{1} \frac{\dd \theta'}{\theta'}
    \int_0^1 \dd z p_i(z)
    \frac{\alpha_S(\kappa)}{\pi}
    \,
    \Theta(X(z,\theta) - x)
    =:
    R_X(x)
    \,.
\end{align}

Furthermore, corrections due to \(\phi(x)\) can also be computed via
\begin{align}
    \int_0^{1} \frac{\dd \theta'}{\theta'}
    \int_0^1 \dd z p_i(z)
    \frac{\alpha_S(\kappa)}{\pi}
    \,
    \phi(x)
    =
    \int_0^{1} \frac{\dd \theta'}{\theta'}
    \int_0^1 \dd z p_i(z)
    \frac{\alpha_S(\kappa)}{\pi}
    \,
    (1 - e^{X(z,\theta)/x})
    -
    \sam{more}
\end{align}
\sam{test further...}

% ---------------------------------------
\Soln{Multiple Emissions SD}{multiple-emissions}
% ---------------------------------------

\sam{Re-evaluate relevance -- there are things here that aren't elsewhere...}

\begin{align}
    \Sigma\left(C_1^{(\beta)}\right) &= \sum_{n = 1}^\infty \prod_{m = 1}^n \left[\int_0^{1} \frac{d\theta'_m}{\theta'_m}\int_0^1 dz_m p_i(z_m) \frac{\alpha_S(\kappa_m)}{\pi}\Theta(z_m - z_c) \Theta(\theta_{m-1} - \theta_m)\right]
    \\
    &\ \ \ \ \times\Theta\left(C_1^{(\beta)} - \sum_{m=1}^n z_m (\theta'_m)^\beta\right) \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right]
\end{align}
where we impose angular ordering with the \(\Theta(\theta_{i-1} - \theta_i)\). Notice that the Laplace transform of this expression is
\begin{align}
    \tilde\Sigma(\nu) &= \int_{-\infty}^\infty d C_1^{(\beta)} \Sigma(C_1^{(\beta)}) e^{-\nu C_1^{(\beta)}}
    \\
    &= \sum_{n=1}^\infty \prod_{m=1}^n  \left[\int_0^{1} \frac{d\theta'_m}{\theta'_m}\int_0^1 dz_m p_i(z_m) \frac{\alpha_S(\kappa_m)}{\pi}\Theta(z_m - z_c) \Theta(\theta_{i-1} - \theta_i)\right]\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right] \times\int^\infty_{C_{\rm max}} dC_1^{(\beta)} e^{-v C_1^{(\beta)}}
\end{align}
where \(C_{\rm max} = \sum_m z_m (\theta'_m)^\beta\), and we have used the \(\Theta\) function. Performing the integral over \(C_1^{(\beta)}\), we have
\begin{align}
    \tilde\Sigma(\nu) &= -\frac{1}{\nu} \sum_{n=1}^\infty \prod_{m=1}^n  \left[\int_0^{1} \frac{d\theta'_m}{\theta'_m}\int_0^1 dz_m p_i(z_m) \frac{\alpha_S(\kappa_m)}{\pi}\Theta(z_m - z_c) \Theta(\theta_{i-1} - \theta_i)\right]\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right] \times \exp\left[ -\nu \sum_m z_m(\theta'_m)^\beta\right]
    \\
    &= -\frac{1}{\nu} \sum_{n=1}^\infty \frac{1}{n!}\left(\int_0^{1} \frac{d\theta'}{\theta'}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c) \right)^n\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right] \times \exp\left[ -\nu \sum_m z_m(\theta'_m)^\beta\right]
    \\
    &= -\frac{1}{\nu} \sum_{n=1}^\infty \frac{1}{n!}\left(\int_0^{1} \frac{d\theta'}{\theta'}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c) \times e^{-\nu z (\theta')^\beta}\right)^n\\
    &\ \ \ \ \ \times \exp\left[-\int_0^1\frac{d\theta}{\theta}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c)\right]
    \\
    &=  -\frac{1}{\nu} \exp\left[\int_0^{1} \frac{d\theta'}{\theta'}\int_0^1 dz p_i(z) \frac{\alpha_S(\kappa)}{\pi}\Theta(z - z_c) \left( e^{-\nu z (\theta')^\beta} - 1 \right)\right]
\end{align}
where we have gained an extra \(\frac{1}{n!}\) by eliminating the angular ordering in the second equality. By replacing \(\beta\) with \(\alpha\), and the theta function \(\Theta(z - z_c)\) with \(\Theta(z - z_c (\theta')^\beta)\), we recover Soft Drop Equations (3.11) and (3.12) (up to a minus sign in the inverse Laplace transform, is this fixed by our clockwise contour?).

>>>>

@@

\begin{exercise*}
    Show that
    \begin{align}
        \abs{\Vec{k}'}
        =
        E'
        =
        E_n + E_{n-1} + \mathcal{O}\le(\theta^2\ri)
        ,
    \end{align}
    and use this to argue that, in the collinear limit, we can parametrize the energy dependence of the differential cross section into dependence on \(E'\) and on \(x\), where \(x\) is an \vocab{energy fraction} defined through
    \begin{align}
        E_n &= x E'
        \\
        E_{n-1} &= (1-x)E'
        .
    \end{align}
    Again, this will hold up to \(\mathcal{O}(\theta^2)\).
\end{exercise*}

@@

    \item
    \label{item:LL_angularity_gen}
    The splitting of a parton is described by its angularity \(e^{(f)}_\varsigma\).
    %
    Using the techniques of the previous section, we may write the LL probability that there is no emission with angularity greater than \(e^{(f)}_\varsigma\), given that there has been an emission with angularity \(e^{(i)}_\varsigma\), as
    \begin{align}
        \label{eq:alg_LLang_ratio}
        \mathbb{P}
        \left(
            {\rm no~emission~with~}e_\varsigma>e^{(f)}_\varsigma
            ~|~
            e_\varsigma < e^{(i)}_\varsigma
        \right)
        &=
        \frac{\Sigma(e^{(f)}_\varsigma)}{\Sigma(e^{(i)}_\varsigma)}
        \\
        \notag
        &=
        \exp\left[
            -\frac{C_R \alphas}{\varsigma~\pi}
            \left(
                \log^2(2 e^{(f)}_\varsigma) - \log^2(2 e^{(i)}_\varsigma)
            \right)
        \right]
        .
    \end{align}
    We can therefore sample from the corresponding probability distribution by the inverse transform method:
    %
    pick a random number \(r\) uniformly distributed between 0 and 1, and set it equal to the above cumulative distribution.
    %
    The corresponding value of \(e^{(f)}_\varsigma\) is
    \begin{align}
        \label{eq:alg_LLang}
        e^{(f)}_\varsigma
        =
        \frac{1}{2}
        \exp\left[
            -\sqrt{\log^2(2 e^{(i)}_\varsigma) - \frac{\varsigma~\pi}{C_R \alphas} \log(r)}
        \right]
        ,
    \end{align}
    which is taken to be the angularity of the splitting from this mother parton.

@@

We can also extend this procedure to include running coupling effects and non-singular pieces of the splitting function, which contribute to MLL accuracy.
%
We produce these higher-order effects by using veto method sampling \cite{Sjostrand:2007gs,Larkoski:2013paa,Sjostrand:2014zea}:
%
\begin{enumerate}
	\item
	\label{item:MLL_ps_start}
	Generate an angularity, angle, and energy fraction with Steps \ref{item:LL_ps_start}--\ref{item:LL_ztheta_sampling} of the LL parton shower algorithm, with the coupling \(\alphas\) of \Eqs{alg_LLang_ratio}{alg_LLang} replaced by a large fixed value for the coupling, \(\hat\alpha = \frac{1}{2}\).

	\item
	As dictated by the veto method, accept the generated variables with a probability given by the ratio \(\rho^{\rm(MLL)}(z,\theta)/\hat\rho^{\rm(LL)}(z,\theta)\), where \(\rho^{\rm(MLL)}\) indicates the MLL probability distribution function and \(\hat\rho^{\rm(LL)}\) indicates the LL probability distribution function with the coupling \(\hat\alpha\).
	%
	In particular, generate a new random number \(r''\) and accept the generated splitting if
	\begin{align}
	    r'' < \mathbb{P}_{\rm no~veto}
	    =
	    \frac{\bar{p}_i(z)}{p_{i,\,\rm gen}(z)}\,\frac{\alphas(\kappa)}{\hat\alpha}
	    ,
	\end{align}
	where \(p_{i,\,\rm gen}(z) = 2 C_{R_i} / z\) is the singular piece of the splitting function, used implicitly in drawing the angularity \(e_\varsigma^{(f)}\) from an LL distribution in \Eq{alg_LLang}.
	%
    The choice \(\hat \alpha = 1/2\) ensures that this probability is less than 1 if we freeze our coupling below the non-perturbative scale \(\mu_{\rm freeze}\) = 1 GeV.

@@

\begin{enumerate}[label=\alph*)]
    \item
    The cumulative distribution for the additive variable \(X\), including contributions from any number of emissions, is
    \begin{align}
        \Sigma(x)
        &=
        \Theta(x)
        +
        \sum_{n = 1}^\infty \prod_{m = 1}^n
        \left[
            \int_0^{\Rjet} \frac{\dd\theta'_m}{\theta'_m}
            \int_0^1 \dd z_m \, p_i(z_m)
            \frac{\alphas(\kappa_m)}{\pi}
            \Theta(\theta_{m-1} - \theta_m)
        \right]
        \,\,\,
        \Theta\left(x - \sum_{m=1}^n X(z_m, \theta_m)\right)
        \,,
    \end{align}
    where the factor of \(\Theta(x)\) on the right-hand side appears because of the possibility that there are no emissions;
    %
    since the splitting functions are plus-function regulated and integrate to zero, proper normalization of \(\Sigma(x)\) implies that the coefficient of \(\Theta(x)\) is one.

    \item
    The Laplace transform, \(\widetilde{f}(\nu) := \int_{-\infty}^\infty \dd x\, f(x) e^{-\nu x}\), of the cumulative distribution is therefore
    \begin{align}
        \widetilde\Sigma(\nu)
        &:=
        \int_{-\infty}^\infty \dd x\, \Sigma(x) e^{-\nu x}
        \\
        &=
        \frac{1}{\nu}
        \,\,+\,\,
        \sum_{n=1}^\infty \prod_{m=1}^n  \left[
            \int_0^{\Rjet} \frac{\dd \theta'_m}{\theta'_m}
            \int_0^1 \dd z_m p_i(z_m)
            \frac{\alphas(\kappa_m)}{\pi}
            \Theta(\theta_{i-1} - \theta_i)
        \right]
        \,\,
        \int^\infty_{\sum X_m} \dd x \, e^{-v x}
        \\
        &=
        \frac{1}{\nu}
        \,\,+\,\,
        \frac{1}{\nu}
        \sum_{n=1}^\infty \prod_{m=1}^n  \left[
            \int_0^{\Rjet} \frac{\dd \theta'_m}{\theta'_m}
            \int_0^1 \dd z_m p_i(z_m)
            \frac{\alphas(\kappa_m)}{\pi}
            \Theta(\theta_{i-1} - \theta_i)
            e^{-v X(z_m, \theta_m)}
        \right]
        \,.
    \end{align}
    Now we can take advantage of angular ordering, using Dyson's trick to replace the product of the factors of \(\Theta(\theta_{i-1} - \theta_i)\) by a single factor of \(1 / n!\).
    %
    Using that the resulting pieces of the integrand have identical forms for each emission (i.e. are independent of \(m\)), this yields
    \begin{align}
        \widetilde\Sigma(\nu)
        &=
        \frac{1}{\nu}
        \,\,
        \sum_{n=0}^\infty \frac{1}{n!}
        \left(
            \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
            \int_0^1 \dd z p_i(z)
            \frac{\alphas(\kappa)}{\pi}
            e^{-v X(z, \theta)}
        \right)^n
        \\
        &=
        \frac{1}{\nu}
        \,\,
        \exp\le[
            \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
            \int_0^1 \dd z p_i(z)
            \frac{\alphas(\kappa)}{\pi}
            e^{-v X(z, \theta)}
        \ri]
        \\
        &=
        \frac{1}{\nu}
        \,\,
        \exp\le[
            \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
            \int_0^1 \dd z p_i(z)
            \frac{\alphas(\kappa)}{\pi}
            \,
            \le(e^{-v X(z, \theta)} - 1\ri)
        \ri]
        \,,
    \end{align}
    where in the final equality we have used that \(p_i(z)\) integrates to zero in the soft-collinear limit.

    Now we must invert the Laplace transform, via
    \begin{align}
        \Sigma(x) = \int \frac{\dd \nu}{2\pi i} \, e^{\nu x} \widetilde\Sigma(\nu)
        \,,
    \end{align}
    to obtain the cumulative distribution for \(X\).
    %
    In particular, we evaluate the inverse Laplace transform for obtaining \(\Sigma(x)\),
    \begin{align}
        \Sigma(x)
        =
        \int \frac{\dd \nu}{2\pi i\, \nu} \, e^{\nu x}
        \,
        \exp\le[
            \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
            \int_0^1 \dd z p_i(z)
            \frac{\alphas(\kappa)}{\pi}
            \,
            \le(e^{-v X(z, \theta)} - 1\ri)
        \ri]
        \,
        :=
        \,
        \int \frac{\dd \nu}{2\pi i\, \nu} \, e^{\nu x}
        \,\,
        \exp \le[-H(1/\nu)\ri]
        \,,
    \end{align}
    where
    \begin{align}
        \label{eq:H-radiator-def}
        H(1/\nu)
        :=
        \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alphas(\kappa)}{\pi}
        \,
        \le(1-e^{-v X(z, \theta)}\ri)
        \,,
    \end{align}
    by the method of steepest descent.

    The integrand is stationary under variations in \(\nu\) when \(\nu = 1/x + \mathcal{O}(\alphas)\), and we will use the following logarithmic Taylor expansion to facilitate the later parts of the calculation:
    \begin{align}
        \label{eq:steepest-descent-expansion-i}
        H(1/\nu)
        =
        H(x)
        +
        \le(\log(\nu) - \log(1/x)\ri)
        \frac{\partial}{\partial\le(\log(\nu')\ri)} H(1/\nu') \Big|_{\nu'=1/x}
        +
        \mathcal{O}\le(\le(\log(\nu) - \log(1/x)\ri)^2\ri)
        \,.
    \end{align}
    Using ``prime'' to denote a derivative with respect to \(\log \nu\) -- or a derivative with respect to \(-\log(x)\) -- we can write \Eq{steepest-descent-expansion-i} in the simpler form
    \begin{align}
        \label{eq:steepest-descent-expansion-ii}
        H(1/\nu)
        =
        H(x)
        +
        \log(x\nu) H'(x)
        +
        \mathcal{O}\le(\log^2(x\nu)\ri)
        \,.
    \end{align}
    Therefore, the full cumulative distribution can be written
    \begin{align}
        \Sigma(x)
        \approx
        \,
        \exp\le[-H(x)\ri]
        \int \frac{\dd \nu}{2\pi i\, \nu} \, e^{\nu x}
        \,\le(x\nu\ri)^{-H'(x)}
        \,\,
    \end{align}
    up to terms of \(\mathcal{O}(H''(x))\).
    %
    Notably, when \(H(x)\) is logarithmic or double logarithmic in \(x\) (as in most practical examples), \(H''(x)\) is zero or constant, respectively;
    %
    therefore, neglecting terms of \(\mathcal{O}(H''(x))\) neglects subleading terms which are not important at leading-logarithmic accuracy.

    Finally, using the given formula for the inverse Laplace transform
    \begin{align}
        \label{eq:inverse-laplace-example}
        \int_{\gamma - i \infty}^{\gamma + i\infty}
        \frac{\dd y}{2\pi i\, y}
        \,
        e^{y} \,y^{-A}
        =
        \frac{1}{\Gamma\le(1 + A\ri)}
        \,,
    \end{align}
    where the value of the integral is the same for all \(\gamma > 0\) is to the right of all singularities of the integrand, we conclude that
    \begin{align}
        \Sigma(x)
        \approx
        \frac{\exp[-H(x)]}{\Gamma\le(1 + H'(x)\ri)}
    \end{align}
    up to terms of \(\mathcal{O}(H''(x))\).

    \item
    It remains to evaluate \(H(x)\).
    %
    We first notice that the factor of \(1 - \exp(-\nu X(z,\theta))\) in \Eq{H-radiator-def} is, for large values of \(\nu = 1/x\), nearly a Heaviside theta function:
    \begin{align}
        \label{eq:exponential-approx-heaviside}
        1 - e^{-\nu X(z,\theta)}
        \xrightarrow[\text{descent}]{\text{steepest}}
        1 - e^{-X(z,\theta)/x}
        =:
        \Theta(X(z,\theta) - x) + \phi(x)
        \,,
    \end{align}
    i.e. that \(\phi(x) := 1 - e^{-X(z,\theta)/x} - \Theta(X(z,\theta) - x)\) is small for small \(x\).
    %
    The first term on the right-hand side of \Eq{exponential-approx-heaviside} therefore directly gives us the radiator \(R_X\) for \(X\) in the expression for \(H(x)\), since
    \begin{align}
        \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alphas(\kappa)}{\pi}
        \,
        \Theta(X(z,\theta) - x)
        =:
        R_X(x)
        \,,
    \end{align}
    or that
    \begin{align}
        H(x)
        =
        R_X(x)
        \, + \,
        \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alphas(\kappa)}{\pi}
        \phi(x)
        =:
        R_X(x) + \delta H(x)
        \,,
    \end{align}
    justifying post-hoc our use of the approximation in \Eq{exponential-approx-heaviside}:
    %
    we see that the leading-logarithmic cumulative distribution for \(X\) is \(\Sigma(x) \approx \exp[-R_X(x)]\), up to sub-leading logarithmic terms dependent on \(R'_X(x)\) and higher derivatives.

    Therefore, for small \(x\) and at leading logarithmic accuracy, we can write \(H(x) \approx R(x)\).

    Our final result, however, must account for corrections due to the nonzero value of \(\phi(x):= 1 - e^{-X(z,\theta)/x} - \Theta(X(z,\theta) - x)\) in \Eq{exponential-approx-heaviside}:
    %
    \begin{subequations}
    \begin{align}
        \delta H(x)
        \,
        &:=
        \,
        \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alphas(\kappa)}{\pi}
        \,
        \phi(x)
        \,
        \\
        &:=
        \,
        \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
        \int_0^1 \dd z p_i(z)
        \frac{\alphas(\kappa)}{\pi}
        \,
        \le[
            (1 - e^{-X(z,\theta)/x})
            -
            \Theta\le(X(z,\theta) - x\ri)
        \ri]
        \,.
    \end{align}
    \end{subequations}

    \item
        When \(X\) is an angularity \(e_\varsigma\) -- i.e. \(X(z,\theta) = z_\text{soft} \theta^\varsigma\), we may compute this final integral over \(\phi(x)\) more explicitly%
        \footnote{
            We will approximate \(z_\text{soft} \approx z\), and ignore any subtleties related to the more correct \(z_\text{soft} = \min(z, 1-z)\) which do not change the form of the results below.
        }.
        %
        We begin by changing variables of integration to \(e' = z \theta^{\prime\,\varsigma}\):
        \begin{align}
            \int_0^{\Rjet} \frac{\dd \theta'}{\theta'}
            \,
            \int_0^1 \dd z \, p(z)
            =
            \frac{1}{\varsigma}
            \int_0^{\Rjet^\varsigma} \frac{\dd e'}{e'}
            \,
            \int_{e'/\Rjet^\varsigma}^1 \dd z \, p(z)
            \,.
        \end{align}
        At MLL, we will also need to remember that the resulting argument of \(\alphas(\kappa) = \alphas(z\theta')\) becomes \(z \theta' = z^{\frac{\varsigma - 1}{\varsigma}} e^{\prime \,\, \frac{1}{\varsigma}}\).

        Our change of variables yields
        \begin{align}
            \delta H(x)
            &=
            \int_0^{\Rjet^\varsigma} \frac{\dd e'}{e'}
            \,
            \int_{e'/\Rjet^\varsigma}^1 \dd z \, p(z)
            \,
            \frac{\alphas(\kappa)}{\varsigma\,\pi}
            \,
            \le[
                (1 - e^{-e'/x})
                -
                \Theta\le(e' - x\ri)
            \ri]
            \\
            &=:
            \int_0^{\Rjet^\varsigma} \frac{\dd e'}{e'}
            \le[
                (1 - e^{-e'/x})
                -
                \Theta\le(e' - x\ri)
            \ri]
            R'(e')
            \\
            &=
            \int_0^{\Rjet^\varsigma}
            \frac{\dd e'}{e'}
            (1 - e^{-e'/x})
            R'(e')
            -
            \int_x^{\Rjet^\varsigma}
            \frac{\dd e'}{e'}
            R'(e')
            \,,
        \end{align}
        where we have used that the radiator for angularities takes the form \(R(e) = \int_e^{\Rjet^\sigma} \dd e' / e' \int_{e'/\Rjet^\varsigma}^1 \dd z \, p(z)\), so that
        \begin{align}
            R'(e_\varsigma)
            =
            -\frac{\dd}{\dd\log e_\varsigma} R(e_\varsigma)
            =
            \int_{e_\varsigma/\Rjet^\varsigma}^1 \dd z \, p(z)
            \,
            \frac{\alphas(\kappa)}{\varsigma\,\pi}
            \,.
        \end{align}
        for angularities.
